### 2013-07-05 Tex/chapters/appendix.tex
Weitere Plots in den Anhang gehängt

\section{Finite Size Scaling at the Example of the Susceptibility and Magnetisation}
\label{appendix:finiteSizeScaling}
    In fig. \ref{fig:gettingCrit:appendix}\subref{sfig:gettingCrit:s_0_sus}
    the magnetic susceptibility
    \[\chi = \frac{1}{TN}\avg{\avg{m^2} - \avg{m}^2}\]
    is plotted and in \ref{fig:gettingCrit:appendix}\subref{sfig:gettingCrit:collapse_s_0_sus}
    collapsed to determine the critical exponent \(\beta\).
    Analog for the mean absolute magnetisation \(\avg{\abs{m}}\) in fig \ref{fig:gettingCrit:appendix}
    \subref{sfig:gettingCrit:s_0_meanM}\subref{sfig:gettingCrit:collapse_s_0_meanM}
    to determine the critical exponent \(\gamma\).
    Both are at \(\sigma=0\) and
    both collapses reproduce the  critical exponent \(\nu\) and the
    critical temperature \(T_c\) in good agreement with the before determined
    values from fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}
    and the analytically known values. This is a good cross check
    for consistency.
    \begin{figure}[htbp]
        \centering
        \subfigure[Susceptibility $\chi$][]
        {
            \label{sfig:gettingCrit:s_0_sus}
            \includegraphics[width=0.47\textwidth]{plots/s_0_sus}
        }
        \subfigure[Finite Size Scaling of the Susceptibility $\chi$][]
        {
            \label{sfig:gettingCrit:collapse_s_0_sus}
            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_sus}
        }
        \subfigure[Magnetisation $\avg{\abs{m}}$][]
        {
            \label{sfig:gettingCrit:s_0_meanM}
            \includegraphics[width=0.47\textwidth]{plots/s_0_meanM}
        }
        \subfigure[Finite Size Scaling of the Magnetisation $\avg{\abs{m}}$][]
        {
            \label{sfig:gettingCrit:collapse_s_0_meanM}
            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_meanM}
        }
        \caption[Examples of determining critical temperature and exponents]
        {
            Examples for finite size scaling.
        }
        \label{fig:gettingCrit:appendix}
    \end{figure}

>>>>

\section{Finite Size Scaling at the Example of the Susceptibility and Magnetisation}
\label{appendix:finiteSizeScaling}
    In fig. \ref{fig:gettingCrit:appendix}\subref{sfig:gettingCrit:s_0_sus}
    the magnetic susceptibility
    \[\chi = \frac{1}{TN}\avg{\avg{E^2} - \avg{E}^2}\]
    is plotted and in \ref{fig:gettingCrit:appendix}\subref{sfig:gettingCrit:collapse_s_0_sus}
    collapsed to determine the critical exponent \(\beta\).
    Analog for the mean absolute magnetisation \(\avg{\abs{m}}\) in fig \ref{fig:gettingCrit:appendix}
    \subref{sfig:gettingCrit:s_0_meanM}\subref{sfig:gettingCrit:collapse_s_0_meanM}
    to determine the critical exponent \(\gamma\).
    Both are at \(\sigma=0\) and
    both collapses reproduce the  critical exponent \(\nu\) and the
    critical temperature \(T_c\) in good agreement with the before determined
    values from fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}
    and the analytically known values. This is a good cross check
    for consistency.
    \begin{figure}[htbp]
        \centering
        \subfigure[Susceptibility $\chi$][]
        {
            \label{sfig:gettingCrit:s_0_sus}
            \includegraphics[width=0.47\textwidth]{plots/s_0_sus}
        }
        \subfigure[Finite Size Scaling of the Susceptibility $\chi$][]
        {
            \label{sfig:gettingCrit:collapse_s_0_sus}
            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_sus}
        }
        \subfigure[Magnetisation $\avg{\abs{m}}$][]
        {
            \label{sfig:gettingCrit:s_0_meanM}
            \includegraphics[width=0.47\textwidth]{plots/s_0_meanM}
        }
        \subfigure[Finite Size Scaling of the Magnetisation $\avg{\abs{m}}$][]
        {
            \label{sfig:gettingCrit:collapse_s_0_meanM}
            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_meanM}
        }
        \caption[Examples of determining critical temperature and exponents]
        {
            Examples for finite size scaling.
        }
        \label{fig:gettingCrit:appendix}
    \end{figure}
